%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                          CONTEXT AND DATA                             %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We begin the section by describing the construction of a ZIP code by month panel
of MW levels in the US.
We use our panel to describe trends in MW policies in the 2010s.
Later, we discuss the relationship between income and housing consumption at the
household level.
We also explore how housing expenditure varies across ZIP codes.
Finally, we document the construction of our analysis sample and discuss
its strengths and limitations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Minimum Wage Policies in the 2010s}
\label{sec:data_mw_panel}

We collect data on federal-, state-, county-, and city-level statutory MW levels 
from \textcite{VaghulZipperer2016}.
We supplement their data, available up to 2016, with data from 
\textcite{BerkeleyLaborCenter} and from official sub-national government offices 
for the years 2016--2020.%
\footnote{Some states and cities issue different MW levels for small businesses
(usually identified by having less than 25 employees).
In these cases, we select the general MW level as the prevalent one.
In addition, there may be different (lower) MW levels for tipped employees.
We do not account for them because employers are typically required to make up 
for the difference between tipped MW plus tips and actual MW.}
%
% Backing up claim on tipped MW: https://www.dol.gov/general/topic/wages/wagestips
%
Most ZIP codes are contained within a jurisdiction, and for them the statutory 
MW is simply the maximum of the federal, state, and local levels.
Some ZIP codes cross jurisdictions, and so are bound by multiple statutory MW 
levels.
In these cases we assign a weighted average of the statutory MW levels in its
constituent census blocks, exploiting an original correspondence table between 
blocks and ZIP codes detailed in Online Appendix \ref{sec:blocks_to_uspszip}, 
where weights correspond to the number of housing units.
The result is a ZIP code-month panel of statutory MW levels in the US between
January 2010 and June 2020.
More details on the construction of the panel can be found in Online Appendix 
\ref{sec:assigning_mw_levels}.

Online Appendix Figure \ref{fig:mw_policies} shows the different levels of 
binding MW policies over time in our data.
Panel A focuses on state-level MW policies.
There are $\stateBindingMW$ states with MW policies in 2010--2020, all of 
which started prior to January 2010.
Panel B shows sub-state MW policies.
In total, there are $\localBindingMW$ counties and cities with some binding MW
policy in this period.
The number of new local jurisdictions instituting a MW policy increases strongly 
after 2013 and declines after 2018.
Overall, we observe strong variations in MW levels across jurisdictions.

Figure \ref{fig:map_mw_perc_changes} maps the percentage change in 
the statutory MW level from January 2010 to June 2020 in each ZIP code.
We observe a great deal of spatial heterogeneity in MW levels within the US.
Importantly, many metropolitan areas across and within state borders have 
differential MW changes, which will be central to distinguishing the effect 
of the two MW-based measures proposed in Section \ref{sec:model}.
We describe the construction of these measures later in this section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relationship Between Income and Housing}
\label{sec:data_income_housing}

We explore the joint-distribution of income levels and housing consumption and
prices in the US using household-level data from the 2011 and 2013 
American Housing Survey \parencite{ahs2020}.
To do so, we compare households within metropolitan areas.
Figure \ref{fig:ahs_pr_renters} shows that low-income households are much
more likely to rent.
While only $\TopDecPrRent$ percent of households in the top income quintile 
are renters, around $\BottomDecPrRent$ percent of them are when focusing on 
the bottom one.
Online Appendix Figure \ref{fig:ahs_rent_sqft} shows that, among households 
that rent, rents per square foot are surprisingly constant across household 
income levels.
Online Appendix Figure \ref{fig:ahs_unit_types} shows the type of building 
households live in by household income decile.

%%
%% Things that we may also say:
%%    - Only one in ten MW workers is a teenager \parencite{Manning2021}.
%%    - 40th of individuals in bottom quintile of individual income are 
%%      household heads
%%

We explore variations over space in housing expenditure.
To do so, for the period 2010--2019
we collected Individual Income Tax Statistics aggregated at the ZIP code 
level from the IRS \parencite{IRS},%
\footnote{For each ZIP code and year we observe the number of households, 
population, adjusted gross income, total wage bill, total business income, 
number of households that receive a wage, number of households that have 
business income, and the number of households with farm income.}
and Small Area Fair Market Rents (SAFMRs hereafter) data from the HUD 
\parencite{hudSAFMR}.%
\footnote{SAFMRs data are constructed by the HUD as an extension of the
Fair Market Rents (FMRs) data using, for each year, ZIP code-level information
from previous years' American Community Survey 
\parencite[][, p.\ 35]{SafmrReport2018}.
SAFMRs are an estimate of the 40th percentile of the rents distribution
based on constant housing quality \parencite[][, p.\ 1]{SafmrReport2018}.
The FMRs data, available at the county and year levels, have been used to study 
the effect of the MW on rents in the US \parencite{Tidemann2018, Yamagishi2019}.}
For each ZIP code in 2018, we constructed a housing expenditure share dividing 
the average monthly wage per household from the IRS by the 2 bedroom SAFMR 
rental value from the HUD.%
\footnote{We impute a small share of missing values using a regression model 
	where the ZIP code-level covariates include data from LODES and the US 
	Census.
	See Online Appendix \ref{sec:measure_housing_expenditure} for details.}%
\textsuperscript{,}%
\footnote{This computation will be a good approximation for the housing 
	expenditure share insofar total housing expenditure and total wage income 
	are roughly proportional to their averages under the same constant of 
	proportionality.
	This computation also assumes away differences in the number of bedrooms 
	across ZIP codes.}
Online Appendix Figure \ref{fig:map_hous_exp_chicago} maps our estimates for the 
metropolitan area of Chicago.
There is considerable variation in housing expenditure over space, with poorer
areas generally spending a higher share of their income in housing.

We would like to know the share of workers earning at or below the MW in each 
ZIP code.
Unfortunately, this variable cannot be constructed from public data.%
\footnote{For instance, in the Current Population Survey (CPS) or the 5\% 
	Census samples available in IPUMS the smallest geographical unit is the 
	Public Use Microdata Area (PUMA).}
Thus, to get a sense of the spatial distribution of minimum wage earners we 
construct a proxy variable using the number of workers across income bins
in the 5-year 2010-2014 American Community Survey \parencite[ACS;][]{CensusACS}.
See details in Online Appendix \ref{sec:assigning_mw_levels}.
Our variable for the share of MW workers is negatively correlated with median 
household income from the ACS (corr.\ $=\corrShWkrMedInc$) and 
positively correlated with our estimate of the housing expenditure share 
(corr.\ $=\corrShWkrS$).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation Data and Samples}

\subsubsection{Rents Data}
\label{sec:data_rents}

One of the main challenges to estimate the effects of any policy on the rental
housing market is to obtain adequate data.
We leverage data from Zillow at the ZIP code and month levels.
The high frequency and resolution of the Zillow data is an advantage since it 
allows us to explore the effects of MW changes on rents exploiting their precise
timing and geographic scope.
Additionally, it allows us to capture current market conditions accurately as it
is computed from newly available housing units.

Zillow is the leading online real estate and rental platform in the US, hosting
more than 110 million homes and 170 million unique monthly users in 2019 
\parencite{ZillowFacts}.
Zillow provides, starting on February 2010, the median rental and sales price 
among homes listed on the platform for different house types and at different 
geographic and time aggregation levels \parencite{ZillowData}.%
\footnote{As of the release of this article, the data are no longer available 
	for download.
	See \textcite{ZillowDataArchive} for a snapshot of the website as of February 
	2020, the last month the data were available.}
We collect the ZIP code level monthly time series from February 2010 to 
December 2019.
There is variation in the entry of a ZIP code to the data, and units with a 
small number of listings are omitted.%
\footnote{Two related notes:
	(i) once a ZIP code enters the Zillow data it never drops out, and
	(ii) the threshold used by Zillow to censor the data is not made public.}

We focus our primary analysis on a single housing category:
Single Family houses, Condominium and Cooperative units (SFCC).
This is the series with the largest number of non-missing ZIP codes, as it 
includes the most common US rental house types \parencite{Fernald2020}.
We focus on rents \textit{per square foot} to account for systematic 
differences in housing size.
In fact, as shown in Online Appendix Figure \ref{fig:ahs_rent_sqft}, this 
variable does not seem to vary much with household income.
Our main outcome variable represents the median rental price per square foot in 
the SFCC category among units listed in the platform for a given ZIP code and 
month.
Online Appendix Figure \ref{fig:trend_zillow_safmr} shows that this series 
follows a similar trend over time when compared to SAFMR.
We show results using median rents per square foot in other rental categories 
available in the data as well.

Our data reflects rents of newly available housing units.
These prices capture market conditions accurately as they incorporate the most
up-to-date information \parencite{AmbroseEtAl2015}.
As a result, we expect them to react quickly to economic shocks, such as 
changes in MW policies.
On the other hand, the rental price of the stock of houses rented would react 
more slowly as contracts are renewed and new information is incorporated in them.
In fact, this is the pattern of results found by \textcite{AgarwalEtAl2021}
when looking at the effect of MW changes on contract rents.

The Zillow data have several limitations.
First, Zillow's market penetration dictates the sample of ZIP codes available.
Online Appendix Figure \ref{fig:map_zillow_sample} shows that the sample of ZIP 
codes with valid SFCC rents data typically coincides with areas of high 
population density.
Second, we only observe the median rental value.
No data on the distribution of rents, nor the number of units listed for rent 
in a given month, are available.
Finally, we observe posted rents rather than contracted rents.
We did not find any data on whether posted rents are a good reflection of 
actually paid rents, so we decided to ask this as a question in the online 
platform Quora.
Online Appendix \ref{sec:posted_rents} shows a selection of quotes from the 
replies, which overwhelmingly suggest that contracted rents generally do not 
differ from posted rents.
A few answers also suggest that rents of long-tenured landlords may not
reflect current market conditions.

\subsubsection{The residence and workplace minimum wage measures}
\label{sec:data_mw_measures}

In this subsection we define the MW variables we use in our analysis,
which follow the intuition in Proposition \ref{prop:representation}.
With the panel described in Section \ref{sec:data_mw_panel} at hand, computing 
the residence MW is straightforward.
We define it as $\mw^{\res}_{it} = \ln \MW_{it}$.

To construct the workplace MW we need to know, for each ZIP code, where workers 
residing in that location work.
We obtain this information from the Longitudinal Employer-Household 
Dynamics Origin-Destination Employment Statistics \parencite[LODES;][]{CensusLODES}
for the years 2009 through 2018.
We collected the datasets for ``All Jobs.''
The raw data are aggregated at the census block level. 
We further aggregate it to ZIP codes using the original correspondence between 
census blocks and USPS ZIP codes described in Online Appendix 
\ref{sec:blocks_to_uspszip}.
This results in ZIP code residence-workplace matrices that, for each location 
and year, indicate the number of jobs of residents in every other location.

We then use the 2017 residence-workplace matrix to build exposure 
weights.
Let $\Z(i)$ be the set of ZIP codes in which $i$'s residents work 
(including $i$).
We construct the set of weights $\{\omega_{iz}\}_{z\in\Z(i)}$ as 
$ \omega_{iz} = N_{iz}/{N_i} , $
where 
$N_{iz}$ is the number of jobs with residence in $i$ and workplace in $z$, 
and $N_i$ is the total number of jobs originating in $i$.
The workplace MW measure is defined as
\begin{equation*}\label{eq:mw_wkp_def}
    \mw^{\wkp}_{it} = \sum_{z\in\Z(i)} \omega_{iz} \ln \MW_{zt} \ .
\end{equation*}
The workplace MW has a shift-share structure, where the log of the MW level
in workplaces can be interpreted as the exogenous shock.
\textcite{BorusyakHullJaravel2021} discuss the interpretation and validity of 
shift-share regressions.
%
% See footnote 13 in BorusyakHullJaravel2021 for a discussion of the non-IV case
%

While our baseline estimates use commuting shares from 2017,
for robustness we present estimates in which the workplace MW measure
is constructed using alternative set of weights.
In particular, we use different years and alternative job categories,
such as jobs for young or low-income workers.%
\footnote{The LODES data reports origin-destination matrices for the number of 
	workers 29 years old and younger, and the number of workers earning less 
	than \$1,251 per month.
The resulting workplace MW measures with any set of weights are highly correlated 
among each other (corr.\ $>0.99$ for every pair).}
%%
%% MG: Documented in descriptive/events_count.
%%

Figure \ref{fig:map_mw_chicago_jul2019}, already discussed in the introduction,
illustrates the difference in these measures by plotting the change in the 
residence and workplace MW measures in the Chicago-Naperville-Elgin CBSA in
July 2019.
For completeness, Online Appendix Figure \ref{fig:map_rents_chicago_jul2019} 
shows the changes in our main median rents variable around the same date.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Other data sources}\label{sec:data_other}

\paragraph{Time-varying data}

To proxy for local economic activity we collect data from the 
Quarterly Census of Employment and Wages \parencite[QCEW;][]{QCEW} 
at the county-quarter and county-month levels for several industrial divisions 
and from 2010 to 2019.%
\footnote{The QCEW covers the following industrial aggregates: 
	``Natural resources and mining,'' ``Construction,'' ``Manufacturing,'' 
	``Trade, transportation, and utilities,'' ``Information,'' 
	``Financial activities'' (including insurance and real state), 
	``Professional and business services,'' ``Education and health services,'' 
	``Leisure and hospitality,'' ``Other services,'' ``Public Administration,''
	and ``Unclassified.''}
We observe, for each county-quarter-industry cell, the number of establishments 
and the average weekly wage, and 
for each county-month-industry cell, the level of employment.
We use these data as controls for the state of the local economy in our 
regression models.

%
% SH: We don't use the RAC-WAC LODES data any longer, so omitting the below. 
%
% We complement the LODES origin-destination matrices with block-level aggregates 
% on residence and workplace area characteristics for the years 2009 through 2018 
% \parencite[also collected from][]{CensusLODES}.
% These data are also aggregated to the ZIP code level following Appendix 
% \ref{sec:blocks_to_uspszip}.
% Relative to the origin-destination matrices, these data contain counts of jobs 
% broken by more detailed categories, such as NAICS industrial aggregates and 
% schooling levels.

\paragraph{ZIP code characteristics}

While our MW assignment recognizes that many of ZIP codes cross census 
geographies, we assign to each ZIP code a unique geography based on where the 
largest share of its houses fall.
We do this for descriptive purposes and also to use geographic indicators  
in our empirical models.

In order to describe our sample of ZIP codes we collect data from the ACS 
\parencite{CensusACS} and the 2010 US Census \parencite{CensusDecennial}.
We collect these data at the block or tract levels, and assign it to ZIP codes
using the correspondence table described in Online Appendix 
\ref{sec:blocks_to_uspszip}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Estimation samples}\label{sec:data_final_panel}

We put together an unbalanced panel of ZIP codes available in Zillow in the 
SFCC category at the monthly date level from February 2010 to December 2019.
This panel contains $\ZIPMWeventsUnbal$ MW changes at the ZIP code level, 
which arise from $\StateMWeventsUnbal$ state-level changes and 
$\CityCountyMWeventsUnbal$ county- and city-level changes.
Online Appendix Figure \ref{fig:mw_changes_dist_zillow} shows the distribution 
of positive increases in our statutory MW variable among all ZIP codes available 
in the Zillow data.
Given that ZIP codes enter the Zillow data progressively over time affecting 
the composition of the sample,
we construct our \textit{baseline panel} keeping ZIP codes that enter at most 
in January 2015.
The resulting fully-balanced panel runs from January 2015 to December 2019
and contains $\ZIPMWeventsBase$ MW changes at the ZIP code level.%
\footnote{To avoid losing observations in models with leads and lags we include 
	six leads and lags of the MW measures, so the dataset actually runs from 
	July 2014 to June 2020.}

Table \ref{tab:stats_zip_samples} compares the sample of ZIP codes in the Zillow
data to the population of ZIP codes along sociodemographic dimensions.
The first and second columns report data for the universe of ZIP codes and 
for the set of urban ZIP codes, respectively.
The third column shows the set of ZIP codes in the Zillow data, i.e., those 
that have some non-missing value of rents per square foot in the SFCC category 
between February 2010 and December 2019.
Finally, the fourth column shows descriptive statistics for our estimation 
sample, which we refer to as the ``baseline sample.''

While our baseline sample contains only 11.8 percent of all urban ZIP codes, it 
covers 25.0 percent of their population and 25.8 percent of their households.
With respect to demographic characteristics, ZIP codes in the baseline sample 
tend to be more populated, richer, with a higher share of Black and Hispanic 
inhabitants, and with a higher share of renter households than both 
the average ZIP code and the average urban ZIP code.
This is the case because Zillow is present in almost every large urban market, 
but it does not operate as often in small urban or rural areas.
In an attempt to capture the treatment effect for the average urban ZIP code 
we conduct an estimation exercise where we re-weight our sample to match the 
average of a handful of characteristics of those.

Finally, Online Appendix Table \ref{tab:stats_est_panel} shows sample statistics 
of our baseline panel.
The distribution of the residence and workplace MW measures is, as expected,
quite similar.
We also show median rents in Zillow in the SFCC category.
The average monthly median rent is \$1,757.9 and \$1.32 per square foot, 
although these variables show a great deal of variation.
Finally, we show average weekly wage, employment, and establishment count 
for the QCEW industries we use as controls in our models.

\paragraph{Auxiliary panels}

For some estimations we construct analogous panels where the units of 
observation are the county by month and ZIP code by year.
In the county by month panel we define the MW measures in an analogous fashion 
as for ZIP codes, and we use Zillow data that is already aggregated at this 
level.
We also define a county-level baseline sample keeping counties with Zillow 
rental data as of January 2015.
In the ZIP code by year panel we compute the monthly difference in log rents 
and MW measures and compute their yearly averages.
