%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                             SETTINGS                                   %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage{inputenc}
\usepackage[style=english]{csquotes}
\usepackage[a4paper, total={6in, 9.2in}]{geometry}
\usepackage{hyperref}
\usepackage{dsfont}
\usepackage{amsmath,amssymb,dsfont}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{indentfirst}
\usepackage[inline]{enumitem}
\usepackage{lscape}
\usepackage[multiple]{footmisc}
\usepackage{babel}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing, positioning, arrows.meta}

\setlength{\parskip}{.5em}%

\usepackage[backend = bibtex,
		   style = authoryear,
		   maxnames = 6,
		   maxcitenames = 3,
		   doi = false,
		   eprint = false]{biblatex}
\addbibresource{../biblio.bib}

\newcommand{\aref}[1]{\hyperref[#1]{Appendix~\ref{#1}}}

\def\equationautorefname~#1\null{%
  equation~(#1)\null
}

\DeclareCiteCommand{\citeyear}
	{}
	{\bibhyperref{\printdate}}
	{\multicitedelim}
	{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                TITLE                                   %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Do Minimum Wages Increase Rents? 
	   Evidence from U.S. ZIP Codes Using High Frequency Data 
	   \thanks{We thank John N. Friedman, Matthew Turner, Jesse M. Shapiro, 
	   	Kenneth Chay, Jesse Bruhn, Neil Thakral, and Matthew Pecenco for numerous 
	   	comments and valuable feedback. All errors are our own.}}
\author{Gabriele Borg \and Diego Gentile Passaro \and Santiago Hermo
		\footnote{
		Borg: Department of Economics, Brown University 
		(email: \url{gabriele_borg@brown.edu}); 
		Gentile Passaro: Department of Economics, Brown University 
		(email: \url{diego_gentile_passaro@brown.edu}); 
		Hermo: Department of Economics, Brown University 
		(email: \url{santiago_hermo@brown.edu}).}
		}
\date{\today}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                              STRUCTURE                                  %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\onehalfspacing
\begin{document}

\maketitle

\begin{abstract}
    \noindent
    In this paper, we estimate the effect of minimum wage policies on housing rental 
    prices. We construct a panel data set at the ZIP code and month level using rents 
    data from Zillow and state and local minimum wage changes between 2010 to 2019. 
    Our baseline empirical approach assumes that unobservable determinants of rents 
    are uncorrelated with past and future minimum wage changes after we condition on 
    proxies for the state of the economy, monthly date and ZIP code fixed effects. 
    Results indicate that increasing the minimum wage by 10 percent is associated with 
    an increase of between 0.25 and 0.5 percent in median rents per square foot. 
    Heterogeneity analysis indicates that the effect is driven by ZIP codes where minimum 
    wage workers reside, with a larger impact in ZIP codes with a high proportion of 
    unemployed, African-American, and younger households. 
    We further create a measure of \textit{experienced minimum wage} which keeps track 
    of the difference between residence and workplace location of low-wage workers. 
    Estimated effects using this measure suggest the presence of income redistribution 
    across ZIP codes following a MW increase, with those in the receiving end 
    experiencing a marked increase in rents. 
    We discuss the magnitude of our main estimates by computing an income-to-rent 
    pass-through for minimum wage legislation of approximately one-third.
\end{abstract}

\vspace{5mm}

\maketitle


\clearpage

\section{Introduction}\label{sec:intro}
    \input{introduction}

\section{Data and Sample Selection Criteria}\label{sec:data}
	\input{data_sample}

\section{Empirical Strategy and Identification}\label{sec:empirical_strategy}
    \input{emp_strategy}

\section{The Effects of Statutory Minimum Wage Changes on Rents}\label{sec:results}
    \input{results}

\section{Tracking Workers: the Experienced Minimum Wage}\label{sec:experienced_mw}
	\input{experienced_mw}

\section{Discussion}\label{sec:discussion}
	\input{discussion}

\section{Conclusions}\label{sec:conclusion}
    \input{conclusion}

 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                                 TAIL                                     %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\printbibliography


\clearpage

\section*{\centering{Appendix}}
\vspace{5mm}

\appendix

\renewcommand\thetable{\thesection.\arabic{table}}    
\renewcommand\thefigure{\thesection.\arabic{figure}} 
\setcounter{table}{0}
\setcounter{figure}{0}
\input{appendix}



\end{document}