%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                             SETTINGS                                  %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage{inputenc}
\usepackage[margin = 1.25in]{geometry}

\usepackage{setspace}
\onehalfspacing

\usepackage{hyperref}
\usepackage{dsfont}
\usepackage{amsmath,amssymb,dsfont,amsthm}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}

\renewcommand{\thesubfigure}{Panel \Alph{subfigure}:}
\captionsetup[subfloat]{labelformat=simple}

\usepackage[inline]{enumitem}
\usepackage{pdflscape}

% Default paths for figures
\graphicspath{{../../analysis/}{../../descriptive/}}

\usepackage[backend = bibtex,
            style = authoryear,
            maxnames = 6,
            maxcitenames = 2,
            doi = false,
            eprint = false]{biblatex}
\addbibresource{../biblio.bib}

% Bibliography
\DeclareCiteCommand{\citeyear}
	{}
	{\bibhyperref{\printdate}}
	{\multicitedelim}
	{}

% To add a comma between consecutive foonotes
\makeatletter
\def\@makefnmark{%
  \leavevmode
  \raise.9ex\hbox{\fontsize\sf@size\z@\normalfont\tiny\@thefnmark}}
\makeatother

% Math-related commands
\newtheorem{assu}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{definition}{Definition}

\newcommand{\Z}{\mathcal{Z}}
\newcommand{\MW}{\underline{W}}
\newcommand{\mw}{\underline{w}}
\newcommand{\wkp}{\text{wkp}}
\newcommand{\res}{\text{res}}
\newcommand{\fed}{\text{fed}}
\newcommand{\pre}{\text{Pre}}
\newcommand{\post}{\text{Post}}
\DeclareMathOperator{\Var}{\mathbb{Var}}
\DeclareMathOperator{\Corr}{\mathbb{Corr}}
\DeclareMathOperator{\Cov}{\mathbb{Cov}}
\DeclareMathOperator{\E}{\mathbb{E}}

% Autofill values
\input{../autofill/output/autofill.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{ Minimum Wage as a Place-Based Policy: \\
        Evidence from US Housing Rental Markets%
        \thanks{We are thankful to Jesse Bruhn, Kenneth Chay, John N.\ Friedman, 
        Peter Hull, Lorenzo Lagos, Rafael La Porta, Bobby Pakzad-Hurson, 
        Matthew Pecenco, Jonathan Roth, Jesse M.\ Shapiro, Neil Thakral, 
        and Matthew Turner for valuable feedback and exchanges during the 
        development of this project.
        We thank three anonymous referees for valuable feedback.
        We also thank seminar participants at 
        the 11th European Meeting of the Urban Economics Association, 
        the Montevideo Graduate Workshop at Universidad Católica del Uruguay, and
        the Applied Micro Lunch at Brown University for valuable comments.
        We acknowledge support from 
        the James M.\ and Cathleen D.\ Stone Wealth and Income Inequality Project and 
        the Orlando Bravo Center for Economic Research, both at Brown University.
        Finally, we thank Martín Gallardo for excellent research assistance.
        All errors are our own.}}

\author{Gabriele Borg \and Diego Gentile Passaro \and Santiago Hermo%
        \footnote{Corresponding author: Santiago Hermo (email: \url{santiago_hermo@brown.edu}).
        Borg: Amazon Web Services;
        Gentile Passaro: Department of Economics, Brown University; 
        Hermo: Department of Economics, Brown University.}}

\date{\today}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                              DOCUMENT                                  %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COVER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract}
    \noindent
    The recent rise of sub-national minimum wage (MW) policies in the US has 
    resulted in significant dispersion of MW levels within metropolitan areas.
    In this paper, we study how commuting patterns determine the effect of 
    MW policies on local rental markets within the city.
    We derive a partial-equilibrium model that suggests a summary statistics 
    approach: the effect of the MW on rents depends on a ``residence'' and a 
    ``workplace'' MW measure.
    We use ZIP-code-by-month rents data and yearly commuting data to estimate 
    the elasticity of rents to each MW measure.
    Our baseline results imply that a 10 percent increase in the workplace MW 
    and no change in the residence MW will increase rents by $\BothBetaBaseTen$ 
    percent.
    If the residence MW also increases by 10 percent, then rents will increase 
    by $\BothSumBaseTen$ percent.
    To illustrate the importance of commuting patterns, we use our estimated 
    elasticities and simulate the impact of federal and city counterfactual 
    MW policies.
    The simulations suggest that landlords pocket approximately 10 cents of each 
    dollar generated by the MW.
    However, the incidence on landlords varies systematically across space.
\end{abstract}

\noindent \textit{JEL codes}: H70, J38, R21, R38.

\noindent \textit{Keywords}: Minimum wages, Housing rents, Place-based policy, Inequality, Spatial Economics.


\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{sec:intro}
    \input{introduction}

\section{A Partial-Equilibrium Model}\label{sec:model}
    \input{model}

\section{Context and Data}\label{sec:data}
    \input{context_data}

\section{Empirical Strategy}\label{sec:empirical_strategy}
    \input{emp_strategy}

\section{Estimation Results}\label{sec:results}
    \input{results}

\section{Counterfactual Analysis}\label{sec:counterfactual}
    \input{counterfactual}

\section{Conclusions}\label{sec:conclusion}
    \input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% BIBLIO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\printbibliography

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIGS & TABS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section*{Figures and Tables}

\input{../figures/map_mw_chicago_jul2019.tex}
\clearpage
\input{../figures/map_mw_perc_changes.tex}
\clearpage
\input{../figures/ahs_pr_renters.tex}
\clearpage
\input{../figures/dynamic_baseline.tex}
\clearpage
\input{../figures/cf_hist_shares.tex}
\clearpage
\input{../figures/map_chicago_cf_shares.tex}
\clearpage
\input{../figures/rho_by_decile_MW_gap.tex}

\clearpage

\input{../tables/output/stats_zip_samples.tex}
\clearpage
\input{../tables/output/static.tex}
\clearpage
\input{../tables/output/robustness.tex}
\clearpage
\input{../tables/output/static_sample.tex}
\clearpage
\input{../tables/output/heterogeneity.tex}
\clearpage
\input{../tables/output/counterfactuals.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\section*{\center{
    Online Appendix for \\
    ``Minimum Wage as a Place-Based Policy: \\
    Evidence from US Housing Rental Markets''}}

\vspace{5mm}

\appendix

\setcounter{page}{1}

\renewcommand\thetable{\arabic{table}} 
\renewcommand\thefigure{\arabic{figure}}
\renewcommand{\tablename}{Online Appendix Table}
\renewcommand{\figurename}{Online Appendix Figure}
\setcounter{table}{0}
\setcounter{figure}{0}

\input{appendix}

\clearpage
\section{Additional Tables and Figures}

\input{../tables/output/stats_est_panel.tex}
\clearpage
\input{../tables/output/autocorrelation.tex}
\clearpage
\input{../tables/output/static_geos_times.tex}
\clearpage
\input{../tables/output/stacked_w6.tex}
\clearpage
\input{../tables/output/arellano_bond.tex}
\clearpage
\input{../tables/output/zillow_categories.tex}
\clearpage
\input{../tables/output/static_wages.tex}

\clearpage

\input{../figures/mw_policies.tex}
\clearpage
\input{../figures/ahs_rent_sqft.tex}
\clearpage
\input{../figures/ahs_unit_types.tex}
\clearpage
\input{../figures/map_housing_exp_chicago_jul2019.tex}
\clearpage
\input{../figures/trend_zillow_safmr.tex}
\clearpage
\input{../figures/map_zillow_sample.tex}
\clearpage
\input{../figures/map_rents_chicago_jul2019.tex}
\clearpage
\input{../figures/mw_changes_dist_zillow.tex}
\clearpage
\input{../figures/non_parametric.tex}
\clearpage
\input{../figures/map_residuals_chicago_jul2019.tex}
\clearpage
\input{../figures/dynamic_county_month.tex}
\clearpage
\input{../figures/dynamic_stacked.tex}
\clearpage
\input{../figures/cf_hist_res_and_wkp_mw.tex}
\clearpage
\input{../figures/map_chicago_cf_wkp_res.tex}
\clearpage
\input{../figures/map_chicago_cf_rents_wages.tex}

\end{document}
